Estimation of Spatiotemporal Integro-Difference Equations for Dynamical Neural Field Models

### 2009-11-13 ltx/BrainIDE.tex
Fixed some more typos in intro

To date, there has been a considerable volume of work in generating physiologically plausible neural field models to fill the void of understanding brain dynamics at the meso/macroscopic scale. Mathematical neural field  models have provided insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008}~\cite{David2003} for recent reviews). These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003},~\cite{Suffczynski2004} and~\cite{Wendling2005} and insights into other pathologies~\cite{Moran2008} that would be impossible to gain from experimental data alone. Unfortunately, to date the use of these models in the clinic has been limited, since the neural field model are constructed for a general brain dynamics and pathologies almost always have unique underlying patient specific causes. Data from EEG and functional magnetic resonance imaging (fMRI) offers the patient specific link to macro-scale cortical dynamics, making these tools readily applicable to the clinic. However the underlying system properties, or system states, are hidden from EEG and fMRI data, making predictions of the underlying physiology inherently difficult.

@@

Recent studies using neural field models have demonstrated the theoretical implications of the connectivity structure of the cortical columns, where the connectivity kernel governs the bifurcation points of the models~\cite{Hutt2005} and types of oscillations that can be generated~\cite{Schmidt2009}. This implies that if we could estimate the connectivity structure for individuals we may be able to model patient specific dynamics. Estimating function cortical connectivity via EEG measures is currently a highly active area of research. There is a lot of interest in understanding the hierarchy of brain regions are involved in specific tasks, motivating the use of techniques like DCM. Other comparable methods are based on auto-regressive (AR) modeling of the times series. Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality~\cite{Hesse2003}, direct transfer function~\cite{Kaminski1991}, partial directed coherence~\cite{Sameshima1999}). Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear between the general field models and the data. Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).

Until now, estimation of local intracortical connectivity structure has not been attempted. Recently it has been shown that it is possible to estimate local coupling of systems governed by integro-difference equations by formulating a state-space model~\cite{Dewar2009}. In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of this technique to neural fields. In this paper we demonstrate for the first time how intracortical connectivity can be inferred from EEG data, based on a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973}. This work provides a fundamental link between the theoretical advances in neural field modeling and patient specific data.

Longrange connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..

\section{Neural Field Model}
In this section we describe a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973} that will be used to create our connectivity estimator. This model has shown to be descriptive of a range of neurodynamics of the cortex such as evoked potentials and epileptic behavior and is capable of generating complex patterns of activity such as Turing patterns, spirals and traveling oscillations. The general form of the model is described here. The post-synaptic potentials generated at a neuronal population $s$ by action potentials arriving from all other connected populations at position $r$ can be described by
\begin{equation}\label{Eq1}
v\left( {s,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)J\left( {r,t'} \right)dt'}.
\end{equation}
The post-synaptic response kernel $h(t)$ is described by
\begin{equation}\label{Eq2}
h(t) = \left\{ {\begin{array}{*{20}{c}}
   {\exp ( - {t \mathord{\left/
 {\vphantom {t \tau }} \right.
 \kern-\nulldelimiterspace} \tau })} & {t \ge 0}  \\
   0 & {t < 0}  \\
\end{array}} \right.,
\end{equation}
where $\tau$ is the synaptic time constant and typically has values from 10-20~ms (\textcolor[rgb]{1.00,0.00,0.00}{refs}). The synaptic response kernel can be more elaborate, using a rise and fall time constant, however this simple form serves our purposes. Equation~\ref{Eq1} relates average firing rate of a presynaptic neural population to the mean membrane potential of the post-synaptic neurons. The mean firing rate, $J$, is convolved with the response kernel to give membrane potential since the firing rate is assumed to follow a (homogeneous?) Poisson process. Nonlocal interactions between cortical populations are described by	
\begin{equation}\label{Eq3}
J\left( {s,t} \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right)
\end{equation}
where $\bar t = t - \frac{{\left| {s - r} \right|}}{d}$, $P$ is a mean pulse rate of population at $y$, $W$ is the connectivity kernel, $E$ is an external input, $\Omega$ is the spatial domain and $d$ is the propagation velocity from $r$ to $s$.

The average firing rate of the presynaptic neurons rate to the pre-synaptic membrane potential by the sigmoid function
\begin{equation}\label{Eq4}
P\left( {v\left( {r,\bar t} \right)} \right) = {R_0}{\left( {1 + \exp \left( {\beta \left( {{v_0}\left( r \right) - v\left( {r,\bar t} \right)} \right)} \right)} \right)^{ - 1}}.
\end{equation}
Even though $v_0$ is a constant, we show express it as a field allowing for inhomogenaities and for clarity in constructing the state-space representation in the next section. The parameters in equation~\ref{Eq4} are... $v_0$ is typically 6~mV, $R_0$ is 5~$s^{-1}$ and $\beta$ is 0.56~mV$^{-1}$ (from Wendling and David papers). By combining equations~\ref{Eq1} and \ref{Eq3} we get the spatiotemporal model
\begin{equation}\label{Eq5}
v\left( {s,t} \right) = \int\limits_{ - \infty }^t {\int\limits_\Omega  {h\left( {t - t'} \right)W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dy} dt'}  + E\left( {s,t} \right).
\end{equation}
To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function
\begin{equation}\label{Eq6}
Lh\left( t \right) = \delta \left( t \right),
\end{equation}
where $L$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. This provides the most general form
\begin{equation}\label{Eq7}
L\left( {\frac{\partial }{{dt}}} \right)v\left( {s,t} \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right),
\end{equation}
where $L$ is a polynomial of order $n$ with constant coefficients. This provides an $n^{th}$ order model. Most studies considering this model use first or second order time derivatives. We shall use the first order model giving
\begin{equation}\label{Eq8}
\frac{{dv\left( {s,t} \right)}}{{dt}} + \frac{{v\left( {s,t} \right)}}{\tau } = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right).
\end{equation}
The neural field model can be represented as a discrete-time stochastic IDE by
\begin{equation}\label{Eq9}
{v_{t + 1}}\left( s \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {{v_{\bar t}}\left( r \right)} \right)dr}  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right),
\end{equation}
where $\epsilon(t)$ is the discrete time stochastic input. The IDE representation of equation~\ref{Eq9} is discrete in time and continuous in space. The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.

\subsection{Assumptions and Simplifications}
We will assume the synaptic response kernel has the same shape (scaled by the connectivity kernel) irrespective of the respective presynaptic population. In this case inhibition can be modeled by having a negative response kernel and excitation with a positive kernel, where the kernel provides the (scaled) polarity. Standing, but not traveling waves? This is a common assumption when dealing with models in this form. We will also assume the velocity of the action potentials is infinite. This is also a common assumption that is made in the neural field modeling community. Recent studies have demonstrated the importance of having a fast, but finite, propagation velocity for models to make realistic and complete predictions of cortical dynamics (Coombes paper, and Atay paper). The purpose of this paper, however, is not to precisely simulate complex cortical dynamics, but to create a useful platform where estimation of hidden states is possible for the purpose of detecting abnormal neural states with intentions of generating informed patient specific control sequences. Therefore, the model simply has to be 'good enough' for this purpose. Starting with this simplified version of the general model is a logical choice. The next assumption we will make is spatial homogeneity such that synaptic interaction between neural populations is only dependant on their spatial separation, and not on their spatial location. Again, this is a common assumption in this field.  This assumption is not essential for our IDE estimation techniques, where a heterogeneous structure is possible. The IDE estimation is derived for a general heterogeneous structure, however for clarity of results we shall only present the heterogeneous case. With these assumptions we have the model in the form
\begin{equation}\label{Eq10}
{v_{t + 1}}\left( s \right) = \int_\Omega  {W\left( {\left| {s - r} \right|} \right)P\left( {{v_t}\left( r \right)} \right)dy}  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right).
\end{equation}
In addition to the assumptions above we shall linearize the model by approximating the sigmoid function $P$ as a piece-wise linear function, $P_{L}$, where
\begin{equation}\label{Eq11}
\begin{array}{*{20}{c}}
   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = 0,} \hfill & {f\left( {{v_t}\left( r \right)} \right) \le 0} \hfill  \\
   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = f\left( {{v_t}\left( r \right)} \right),} \hfill & {0 < f\left( {{v_t}\left( r \right)} \right) < {R_0}} \hfill  \\
   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = {R_0},} \hfill & {f\left( {{v_t}\left( r \right)} \right) \ge {R_0}} \hfill  \\
\end{array}
\end{equation}
and
\begin{equation}\label{Eq12}
f\left( {{v_t}\left( r \right)} \right) = \frac{{{R_0}}}{2}\left( {1 + \frac{\beta }{2}\left( {{v_t}\left( r \right) - {v_0}\left( r \right)} \right)} \right).
\end{equation}
For the derivation of the state-space model we shall assume that the model is operating in the active dynamic region, since this is the most interesting case, and the other cases correspond to the neural populations either being saturated (at $R_0$) or being silent. We shall show be stability analysis that the model will not saturate for the given parameters and nor will it be silent since it is continuously driven by noise. Substituting equation~\ref{Eq11} into equation~\ref{Eq10} and expanding we get
\begin{align}\label{Eq13}
 {v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}\int_\Omega  {W\left( {\left| {s - r} \right|} \right){{\bar v}_0}\left( r \right)dr}  \nonumber \\
  + \frac{{{R_0}}}{2}\beta \int_\Omega  {W\left( {\left| {s - r} \right|} \right){v_t}\left( r \right)dr}  \\
  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right), \nonumber
\end{align}
where ${\bar v_0}\left( r \right) = 1 - \frac{\beta }{2}{v_0}\left( r \right)$.

@@

where $\Theta \in \mathbb{R}^n$ is a vector of unknown parameters (amplitudes of kernels), $\psi(s,r)$ is a matrix that can be considered a field that is scaled by $\Theta$, and $\phi(s)$ is a vector of basis functions that decomposes the field and $x_t \in\mathbb{R}^n$ is the state vector at sampling time $t$. The voltage field at $t$ is comprised of a scaled version (by the state $x_t$) of the basis functions $\phi(s)$.

>>>>

To date, there has been a considerable volume of work in generating physiologically plausible neural field models to fill the void of understanding brain dynamics at the meso/macroscopic scale. Mathematical neural field  models have provided insights into the underlying physics and dynamics of electroencephalography (EEG) and magnetoencephalography (MEG) (see~\cite{Deco2008}~\cite{David2003} for recent reviews). These models have demonstrated possible mechanisms for the genesis of neural rhythms (such as the alpha and gamma rhythms) \cite{Liley1999} \cite{RENNIE2000}, epileptic seizure generation \cite{DaSilva2003},~\cite{Suffczynski2004} and~\cite{Wendling2005} and insights into other pathologies~\cite{Moran2008} \cite{Schiff2009} that would be impossible to gain from experimental data alone. Unfortunately, to date the use of these models in the clinic has been limited, since the neural field model are constructed for a general brain dynamics and pathologies almost always have unique underlying patient specific causes. Data from EEG and functional magnetic resonance imaging (fMRI) offers the patient specific link to macro-scale cortical dynamics, making these tools readily applicable to the clinic. However the underlying system properties, or system states, are hidden from EEG and fMRI data, making predictions of the underlying physiology inherently difficult.

@@

Recent studies using neural field models have demonstrated the theoretical implications of the connectivity structure of the cortical columns, where the connectivity kernel governs the bifurcation points of the models~\cite{Hutt2005} and types of oscillations that can be generated~\cite{Schmidt2009}. This implies that if we could estimate the connectivity structure for an individual, than we could model patient specific neurodynamics. Estimating functional cortical connectivity via EEG measures is currently a highly active area of research. There is a lot of interest in understanding the hierarchy of brain regions are involved in specific tasks, motivating the use of techniques like DCM. Other comparable methods are based on auto-regressive (AR) modeling of the EEG, MEG or fMRI times series. Studies have concentrated on finding functional connectivity patterns using information contained in the AR coefficients using techniques like Granger causality~\cite{Hesse2003}, the direct transfer function~\cite{Kaminski1991}, and partial directed coherence~\cite{Sameshima1999}). Again, like the DCM approach, these methods estimate long range connectivity patterns that does not provide a clear relationship between the continuum field models and data. Analysis of the connectivity estimates provided from these approaches has involved graph theoretical techniques (small worldedness).

Until now, estimation of local intracortical connectivity structure has not been attempted. Recently, it has been shown that it is possible to estimate local coupling of systems governed by integro-difference equations by formulating a state-space model~\cite{Dewar2009}. The key development in this work was to define the state-space model order independent of the number of observations (or ECoG recording electrodes in this case). In addition, the appropriate model selection tools have been developed~\cite{Scerri2009} allowing for the application of this technique to neural fields. Modeling the neural dynamics within this framework has a distinct advantage over AR models, such that the number of parameters to define the connectivity basis functions is considerably smaller than the number of AR coefficients typically required to achieve the relevant information criteria. In this paper we demonstrate for the first time how intracortical connectivity can be inferred from ECoG data, based on a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973}. This work provides a fundamental link between the theoretical advances in neural field modeling and patient specific data.

Long range connectivity can be estimated using DTI~\cite{Knock2009}, however this short range connectivity can not..

\section{Neural Field Model}
In this section we describe a variant of the  Wilson and Cowan neural field model~\cite{Wilson1973} that will be used to create our connectivity estimator. This model has shown to be descriptive of a range of neurodynamics of the cortex such as evoked potentials, visual hallucinations and epileptic behavior. It is also capable of generating complex patterns of activity such as Turing patterns, spirals and traveling oscillations. The general form of the model is described here. The post-synaptic potentials generated at a neuronal population $s$ by action potentials arriving from all other connected populations at position $r$ can be described by
\begin{equation}\label{Eq1}
v\left( {s,t} \right) = \int_{ - \infty }^t {h\left( {t - t'} \right)J\left( {r,t'} \right)dt'}.
\end{equation}
The post-synaptic response kernel $h(t)$ is described by
\begin{equation}\label{Eq2}
h(t) = \left\{ {\begin{array}{*{20}{c}}
   {\exp ( - {t \mathord{\left/
 {\vphantom {t \tau }} \right.
 \kern-\nulldelimiterspace} \tau })} & {t \ge 0}  \\
   0 & {t < 0}  \\
\end{array}} \right.,
\end{equation}
where $\tau$ is the synaptic time constant and typically has values from 10-20~ms (\textcolor[rgb]{1.00,0.00,0.00}{refs}). The synaptic response kernel can be more elaborate, using a rise and fall time constant, however this simple form serves our purposes. Equation~\ref{Eq1} relates average firing rate of a presynaptic neural population to the mean membrane potential of the post-synaptic neurons. The mean firing rate, $J$, is convolved with the response kernel to give membrane potential since the firing rate is assumed to follow a (homogeneous?) Poisson process. Nonlocal interactions between cortical populations are described by	
\begin{equation}\label{Eq3}
J\left( {s,t} \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right)
\end{equation}
where $\bar t = t - \frac{{\left| {s - r} \right|}}{d}$, $P$ is a mean pulse rate of population at $y$, $W$ is the connectivity kernel, $E$ is an external input, $\Omega$ is the spatial domain and $d$ is the propagation velocity from $r$ to $s$.

The average firing rate of the presynaptic neurons rate to the pre-synaptic membrane potential by the sigmoid function
\begin{equation}\label{Eq4}
P\left( {v\left( {r,\bar t} \right)} \right) = {R_0}{\left( {1 + \exp \left( {\beta \left( {{v_0}\left( r \right) - v\left( {r,\bar t} \right)} \right)} \right)} \right)^{ - 1}}.
\end{equation}
Even though $v_0$ is a constant, we show express it as a field allowing for inhomogeneities and for clarity in constructing the state-space representation in the next section. The parameters in equation~\ref{Eq4} are... $v_0$ is typically 6~mV, $R_0$ is 5~$s^{-1}$ and $\beta$ is 0.56~mV$^{-1}$ (from Wendling and David papers). By combining equations~\ref{Eq1} and \ref{Eq3} we get the spatiotemporal model
\begin{equation}\label{Eq5}
v\left( {s,t} \right) = \int\limits_{ - \infty }^t {\int\limits_\Omega  {h\left( {t - t'} \right)W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dy} dt'}  + E\left( {s,t} \right).
\end{equation}
To arrive at the final form of the model we shall state the synaptic response kernel as a Green's function
\begin{equation}\label{Eq6}
Lh\left( t \right) = \delta \left( t \right),
\end{equation}
where $L$ is a temporal differential operator and $\delta(t)$ is the Dirac-delta function. This provides the most general form
\begin{equation}\label{Eq7}
L\left( {\frac{\partial }{{dt}}} \right)v\left( {s,t} \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right),
\end{equation}
where $L$ is a polynomial of order $n$ with constant coefficients. This provides an $n^{th}$ order model. Most studies considering this model use first or second order time derivatives. We shall use the first order model giving
\begin{equation}\label{Eq8}
\frac{{dv\left( {s,t} \right)}}{{dt}} + \frac{{v\left( {s,t} \right)}}{\tau } = \int_\Omega  {W\left( {s,r} \right)P\left( {v\left( {r,\bar t} \right)} \right)dr}  + E\left( {s,t} \right).
\end{equation}
The neural field model can be represented as a discrete-time stochastic IDE by
\begin{equation}\label{Eq9}
{v_{t + 1}}\left( s \right) = \int_\Omega  {W\left( {s,r} \right)P\left( {{v_{\bar t}}\left( r \right)} \right)dr}  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right),
\end{equation}
where $\epsilon(t)$ is the discrete time stochastic input. The IDE representation of equation~\ref{Eq9} is discrete in time and continuous in space. The neural field model is popular due to being parsimonious yet having a strong link with the underlying physiology.

\subsection{Assumptions and Simplifications}
We will assume the synaptic response kernel has the same shape (scaled by the connectivity kernel) irrespective of the respective presynaptic population. In this case inhibition can be modeled by having a negative response kernel and excitation with a positive kernel, where the kernel provides the (scaled) polarity. This reduced the model to a single field. I am not sure how this will limit the dynamics?? We will also assume the velocity of the action potentials is infinite. This is also a common assumption that is made when modeling intracortical circuits. As stated in Wilson and Cohen's original works, the time constant $\tau$ is much greater than the axonal propagation delays, therefore it is reasonable to approximate the the delays as being infinite. Recent studies have demonstrated the importance of having a fast, but finite, propagation velocity for models to make realistic and complete predictions of cortical dynamics (Coombes paper, and Atay paper). The purpose of this paper, however, is not to precisely simulate complex cortical dynamics, but to create a useful platform where estimation of hidden states is possible for the purpose of detecting abnormal neural states with intentions of generating informed patient specific control sequences. Therefore, the model simply has to be 'good enough' for this purpose. Starting with this simplified version of the general model is a logical choice. The next assumption we will make is spatial homogeneity such that synaptic interaction between neural populations is only dependant on their spatial separation, and not on their spatial location. Again, this is a common assumption when dealing with intracortical connectivity. This assumption is not essential for our IDE estimation techniques, where a heterogeneous structure is possible. The IDE estimation is derived for a general heterogeneous structure, however for clarity of results we shall only present the heterogeneous case. With these assumptions we have the model in the form
\begin{equation}\label{Eq10}
{v_{t + 1}}\left( s \right) = \int_\Omega  {W\left( {\left| {s - r} \right|} \right)P\left( {{v_t}\left( r \right)} \right)dy}  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right).
In addition to the assumptions above we shall linearize the model by approximating the sigmoid function $P$ as a piece-wise linear function, $P_{L}$, where
\begin{equation}\label{Eq11}
\begin{array}{*{20}{c}}
   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = 0,} \hfill & {f\left( {{v_t}\left( r \right)} \right) \le 0} \hfill  \\
   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = f\left( {{v_t}\left( r \right)} \right),} \hfill & {0 < f\left( {{v_t}\left( r \right)} \right) < {R_0}} \hfill  \\
   {{P_{L}}\left( {{v_t}\left( r \right)} \right) = {R_0},} \hfill & {f\left( {{v_t}\left( r \right)} \right) \ge {R_0}} \hfill  \\
\begin{equation}\label{Eq12}
f\left( {{v_t}\left( r \right)} \right) = \frac{{{R_0}}}{2}\left( {1 + \frac{\beta }{2}\left( {{v_t}\left( r \right) - {v_0}\left( r \right)} \right)} \right).
For the derivation of the state-space model we shall assume that the model is operating in the active dynamic region, since this is the most interesting case, and the other cases correspond to the neural populations either being saturated (at $R_0$) or being silent. We shall show be stability analysis that the model will not saturate for the given parameters and nor will it be silent since it is continuously driven by noise. Substituting equation~\ref{Eq11} into equation~\ref{Eq10} and expanding we get
\begin{align}\label{Eq13}
 {v_{t + 1}}\left( s \right) = \frac{{{R_0}}}{2}\int_\Omega  {W\left( {\left| {s - r} \right|} \right){{\bar v}_0}\left( r \right)dr}  \nonumber \\
  + \frac{{{R_0}}}{2}\beta \int_\Omega  {W\left( {\left| {s - r} \right|} \right){v_t}\left( r \right)dr}  \\
  + {\varepsilon _t}\left( s \right) - \frac{1}{\tau }{v_t}\left( s \right), \nonumber
where ${\bar v_0}\left( r \right) = 1 - \frac{\beta }{2}{v_0}\left( r \right)$.

Alternatively we replace the sigmoidal firing mechanism with a Heaviside function.

@@

where $\theta \in \mathbb{R}^n$ is a vector of unknown parameters (amplitudes of kernels), $\psi(s,r)$ is a matrix that can be considered a field that is scaled by $\theta$, and $\phi(s)$ is a vector of basis functions that decomposes the field and $x_t \in\mathbb{R}^n$ is the state vector at sampling time $t$. The voltage field at $t$ is comprised of a scaled version (by the state $x_t$) of the basis functions $\phi(s)$.
